\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-25 doc/paper.Rmd
mini edit ...

cvcs %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo), 
             shape=factor(wv), linetype=method)) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_shape_discrete("Method", expression("Validation\nwindow size"~w[v])) +
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~wv, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)") +
  guides(
   colour = guide_legend(order = 3, ncol=2),
   linetype = guide_legend(order = 1, ncol=2),
   shape = guide_legend(order = 2, ncol=2)
 )

@@

\autoref{fig:type1} shows observed type I error rates across a range of optimization windows $w_o$. Generally, observed type I errors are higher than expected, but with an increase in the size of the optimization window observed type I error rates decrease.

@@

dt <- rbind(wo120_sig, wo120_pr) %>% 
  ungroup() %>% 
  mutate(beta = round(100*beta, 1)) %>%
  dplyr::select(wv, type, alpha, beta) %>% 
  spread(alpha, beta)
print(xtable(dt), include.rownames=FALSE)
```

\begin{table}[ht]
\caption{\label{tab:type2} Type II error rates for profiles and signatures of bullet lands. For profiles, a coarseness value of $c = 0.25$ is used to remove bullet curvature.}
\centering
\begin{tabular}{rlrrrr}
  \hline
validation && \multicolumn{4}{l}{Nominal type I error rate $\alpha$}\\  
window $w_v$ & source & 0.001 & 0.005 & 0.01 & 0.05 \\ 
  \hline
 30 & profiles & 54.40 & 43.80 & 39.70 & 30.00 \\ 
   30 & signatures & 55.00 & 45.40 & 41.40 & 31.10 \\ \hline
   50 & profiles & 58.50 & 44.40 & 40.70 & 28.70 \\ 
   50 & signatures & 62.60 & 49.60 & 44.20 & 30.50 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

cvcs %>% 
  ggplot(aes(d = as.numeric(!match), m = p_value, colour=factor(wo), 
             shape=factor(wv), linetype=method)) + 
  geom_roc(labels=FALSE, n.cuts=100, pointsize=0, size=0.6) +
  geom_abline(
    linetype=3, slope=-1, intercept = 1, colour="grey30", size=.3) +
  theme_bw() + 
  scale_shape_discrete("Method", expression("Validation\nwindow size"~w[v])) +
  scale_linetype_discrete("Method") + 
  scale_colour_brewer(
    expression("Optimization\nwindow size"~w[o]), palette="Set2") +
  facet_grid(.~wv, labeller="label_both") +
  xlab("False Positives Rate (1 - Specificity)") +
  ylab("True Positives Rate (Sensitivity)") +
  guides(
   colour = guide_legend(order = 3, ncol=2),
   linetype = guide_legend(order = 1, ncol=2),
   shape = guide_legend(order = 2, ncol=2)
 )

@@

\autoref{fig:type1} shows observed type I error rates across a range of optimization windows $w_o$. Generally, observed type I errors are higher than expected. Method CS1 shows in this instance slightly better performance than method CS2, but for both an increase in the size of the optimization window leads to a decrease in the observed type I error rates.

@@

dt <- rbind(wo120_sig, wo120_pr) %>% 
  ungroup() %>% 
  mutate(beta = round(100*beta, 1)) %>%
  dplyr::select(wv, type, alpha, beta) %>% 
  spread(alpha, beta)
print(xtable(dt), include.rownames=FALSE)
```
<!--
\begin{table}[ht]
\caption{\label{tab:type2} Type II error rates for profiles and signatures of bullet lands. For profiles, a coarseness value of $c = 0.25$ is used to remove bullet curvature.}
\centering
\begin{tabular}{rlrrrr}
  \hline
validation && \multicolumn{4}{l}{Nominal type I error rate $\alpha$}\\  
window $w_v$ & source & 0.001 & 0.005 & 0.01 & 0.05 \\ 
  \hline
 30 & profiles & 54.40 & 43.80 & 39.70 & 30.00 \\ 
   30 & signatures & 55.00 & 45.40 & 41.40 & 31.10 \\ \hline
   50 & profiles & 58.50 & 44.40 & 40.70 & 28.70 \\ 
   50 & signatures & 62.60 & 49.60 & 44.20 & 30.50 \\ 
   \hline
\end{tabular}
\end{table}
-->

### 2018-04-25 doc/paper.tex
figures 9 and 10
mini edit ...

{\centering \includegraphics[width=0.6\textwidth]{figures/type2-1}

@@

{\centering \includegraphics[width=0.6\textwidth]{figures/roc-1}

@@

\autoref{fig:type1} shows observed type I error rates across a range of
optimization windows \(w_o\). Generally, observed type I errors are
higher than expected, but with an increase in the size of the
optimization window observed type I error rates decrease.

@@

\begin{table}[ht]
\caption{\label{tab:type2} Type II error rates for profiles and signatures of bullet lands. For profiles, a coarseness value of $c = 0.25$ is used to remove bullet curvature.}
\centering
\begin{tabular}{rlrrrr}
  \hline
validation && \multicolumn{4}{l}{Nominal type I error rate $\alpha$}\\  
window $w_v$ & source & 0.001 & 0.005 & 0.01 & 0.05 \\ 
  \hline
 30 & profiles & 54.40 & 43.80 & 39.70 & 30.00 \\ 
   30 & signatures & 55.00 & 45.40 & 41.40 & 31.10 \\ \hline
   50 & profiles & 58.50 & 44.40 & 40.70 & 28.70 \\ 
   50 & signatures & 62.60 & 49.60 & 44.20 & 30.50 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

{\centering \includegraphics[width=0.9\textwidth]{figures/type2-1}

@@

{\centering \includegraphics[width=\textwidth]{figures/roc-1}

@@

\autoref{fig:type1} shows observed type I error rates across a range of
optimization windows \(w_o\). Generally, observed type I errors are
higher than expected. Method CS1 shows in this instance slightly better
performance than method CS2, but for both an increase in the size of the
optimization window leads to a decrease in the observed type I error
rates.

@@
